%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
		%---------------------------------------------------------
	\cventry
	{Project Engineer} % Job title
	{Abu Dhabi Police} % Organization
	{UAE} % Location
	{March 2024 - Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item Implemented a monitoring solution using Elasticsearch and Kibana to improve monitoring capabilities and generate reports.
            \item Visualised server statistics for stakeholders using Kibana.
			\item Improved overall efficiency by 45\%.
		\end{cvitems}
	}
	
	\cventry
 	{Project Engineer} % Job title
	{Midis Group} % Organization
	{UAE} % Location
	{March 2024 - Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item Working on site to provide support to the client.
		\end{cvitems}
  }
  \cventry
	{Big Data Intern} % Job title
	{Midis Group} % Organization
	{UAE} % Location
	{May 2023 - March 2024} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item Created data reports on tickets raised and solved by the team for stakeholders.
			\item Implemented Python scripts to improve customers' workflows
			\item Created Hadoop distributed computing clusters and improved customer big data management by 70\%.
			\item Improved data mining and analysis  workflows for customers.
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	\cventry
	{Intern} % Job title
	{Heriot-Watt University} % Organization
	{Dubai} % Location
	{Sept. 2022 - May 2023} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item Mentored 50+ students in Python, machine learning algorithms,  data visualization techniques, Jupyter, networking tools, VMs, Java, and other tools to enhance their practical skills by leading regular labs.
			\item Assisted professors in various courses taken under the Computer Science program at the university.
			\item  Analysed student performance in the courses and created reports on overall class performance for professors.
		\end{cvitems}
	}
	
	%---------------------------------------------------------
\end{cventries}
